\newpage
\setstretch{1.0}

%\PassOptionsToPackage{hyphens}{url}
%\expandafter\def\expandafter\UrlBreaks\expandafter{\UrlBreaks% save the current one
%	\do\a\do\b\do\c\do\d\do\e\do\f\do\g\do\h\do\i\do\j%
%	\do\k\do\l\do\m\do\n\do\o\do\p\do\q\do\r\do\s\do\t%
%	\do\u\do\v\do\w\do\x\do\y\do\z\do\A\do\B\do\C\do\D%
%	\do\E\do\F\do\G\do\H\do\I\do\J\do\K\do\L\do\M\do\N%
%	\do\O\do\P\do\Q\do\R\do\S\do\T\do\U\do\V\do\W\do\X%
%	\do\Y\do\Z\do\*\do\-\do\~\do\'\do\"\do\-}%

\begin{flushleft}

\begin{thebibliography}{99}
\addcontentsline{toc}{section}{Reference}


\bibitem{dotnetApi} .NET API browser | Microsoft Docs. [online]. [cit.~19.12.2020]. Dostupné z: \url{https://docs.microsoft.com/en-us/dotnet/api/?view=netframework-4.8}

\bibitem{winformsObselote5} .NET -- When creating a new GUI, is WPF the preferred choice over Windows Forms? -- Stack Overflow. [online] [cit.~18.12.2020]. Dostupné z: \url{https://stackoverflow.com/questions/57909/when-creating-a-new-gui-is-wpf-the-preferred-choice-over-windows-forms}

\bibitem{winformsDpiScaling} .NET -- WinForms 4K and 1080p scaling / high DPI? -- Stack Overflow. [online] [cit.~26.2.2021]. Dostupné z: \url{https://stackoverflow.com/questions/49012233/winforms-4k-and-1080p-scaling-high-dpi}

\bibitem{seleniumWhyUse} 16 reasons why to use Selenium IDE in 2019 (and 2 why not) -- Automated Visual Testing | Applitools. [online] [cit.~14.11.2020]. Dostupné z: \url{https://applitools.com/blog/why-selenium-ide-2019}

\bibitem{seleniumAbout} About Selenium. SeleniumHQ Browser Automation. [online] [cit.~2.5.2020]. Dostupné z: \url{https://www.selenium.dev/about}

\bibitem{nodejs} About | Node.js. [online] [cit.~30.10.2020]. Dostupné z: \url{https://nodejs.org/en/about}

\bibitem{phantomJsArchiving} Archiving the project: suspending the development · Issue \#15344 · ariya/phan\-tomjs · GitHub. [online] [cit.~7.11.2020]. Dostupné z: \url{https://github.com/ariya/phantomjs/issues/15344}

\bibitem{headless} Automated testing with Headless Chrome | Google Developers. [online] [cit.~2.5.2020]. Dostupné z: \url{https://developers.google.com/web/updates/2017/06/headless-karma-mocha-chai}

\bibitem{firefoxExtensionCompatibility}
Browser Extensions -- Mozilla | MDN. [online] [cit.~23.1.2021]. Dostupné z: \url{https://developer.mozilla.org/en-US/docs/Mozilla/Add-ons/WebExtensions}

\bibitem{browsingContextMozillaDevs} Browsing Context | MDN. [online] [cit.~7.11.2020]. Dostupné z: \url{https://developer.mozilla.org/en-US/docs/Glossary/Browsing_context}

\bibitem{uwpSupportedPlatforms} Choose your Windows app platform -- Windows applications | Microsoft Docs. [online] [cit.~19.12.2020]. Dostupné z: \url{https://docs.microsoft.com/en-us/windows/apps/desktop/choose-your-platform}

\bibitem{extensionAPI2} Chrome APIs -- Google Chrome. [online] [cit.~2.5.2020]. Dostupné z: \url{https://developer.chrome.com/extensions/api_index}

\bibitem{devtools} Chrome DevTools | Google Developers. [online] [cit.~	2.5.2020]. Dostupné z: \url{https://developers.google.com/web/tools/chrome-devtools}

\bibitem{devtoolsProtocol} Chrome DevTools Protocol. [online] [cit.~2.11.2020]. Dostupné z: \url{https://chromedevtools.github.io/devtools-protocol}

\bibitem{ranorexAbout} Company Profile | About Ranorex. [online] [cit.~9.12.2020]. Dostupné z: \url{https://www.ranorex.com/company}

\bibitem{monoCompatibility} Compatibility | Mono. [online]. [cit.~19.12.2020]. Dostupné z: \url{https://www.mono-project.com/docs/about-mono/compatibility}

\bibitem{seleniumEcosystem} Ecosystem. SeleniumHQ Browser Automation. [online] [cit.~31.10.2020]. Dostupné z: \url{https://www.selenium.dev/ecosystem}

\bibitem{electron} Electron | Build cross-platform desktop apps with JavaScript, HTML, and CSS. [online] [cit.~14.11.2020]. Dostupné z: \url{https://www.electronjs.org}

\bibitem{elementObject} Element -- Web APIs | MDN. [online] [cit.~13.12.2020]. Dostupné z: \url{https://developer.mozilla.org/en-US/docs/Web/API/Element}

\bibitem{firefoxReleaseCalendar} Firefox Release Calendar -- MozillaWiki. [online] [cit.~8.11.2020]. Dostupné z: \url{https://wiki.mozilla.org/Release_Management/Calendar}

\bibitem{firefoxLegacyExtensions} Frequently asked questions -- Firefox add-on technology is modernizing | Firefox Help. [online] [cit.~14.11.2020]. Dostupné z: \url{https://support.mozilla.org/en-US/kb/frequently-asked-questions-firefox-addon}

\bibitem{headlessChromeGettingStarted} Getting Started with Headless Chrome | Google Developers. [online] [cit.~7.11.2020]. Dostupné z: \url{https://developers.google.com/web/updates/2017/04/headless-chrome}

\bibitem{checkly} GitHub -- checkly/headless-recorder. [online] [cit.~30.10.2020]. Dostupné z: \url{https://github.com/checkly/headless-recorder}

\bibitem{scintillaGithub} GitHub -- jacobslusser/ScintillaNET. [online] [cit.~14.1.2021]. Dostupné z: \url{https://github.com/jacobslusser/ScintillaNET}

%\bibitem{projectGithub} GitHub - Kubikola/puppeteer-automation. [online] [cit.~28.1.2021]. Dostupné z: \url{https://github.com/Kubikola/puppeteer-automation}

\bibitem{playwrightGithub} GitHub -- microsoft/playwright. [online] [cit.~5.11.2020]. Dostupné z: \url{https://github.com/microsoft/playwright}

\bibitem{seleniumIdeGithub} GitHub -- SeleniumHQ/selenium-ide v3. [online] [cit.~14.11.2020]. Dostupné z: \url{https://github.com/SeleniumHQ/selenium-ide/tree/v3}

\bibitem{crlzmq4} GitHub -- zeromq/clrzmq4. [online] [cit.~19.12.2020]. Dostupné z: \url{https://github.com/zeromq/clrzmq4}

\bibitem{netmqGithub} GitHub -- zeromq/netmq. [online] [cit.~19.12.2020]. Dostupné z: \url{https://github.com/zeromq/netmq}

\bibitem{zeromqJs} GitHub -- zeromq/zeromq.js: Node.js bindings to the ØMQ library. [online] [cit.~19.12.2020]. Dostupné z: \url{https://github.com/zeromq/zeromq.js}

\bibitem{googleChromeReleases} Google Chrome version history -- Wikipedia. [online] [cit.~8.11.2020]. Dostupné z: \url{https://en.wikipedia.org/wiki/Google_Chrome_version_history}

\bibitem{enableTrueRemoteDebuggingChrome} Google Chrome -- Using Chromium Remote Debugging from External Device -- Stack Overflow. [online] [cit.~4.1.2021]. Dostupné z: \url{https://stackoverflow.com/questions/18506233/using-chromium-remote-debugging-from-external-device}

\bibitem{htmlElementObject} HTMLElement -- Web APIs | MDN. [online] [cit.~13.12.2020]. Dostupné z: \url{https://developer.mozilla.org/en-US/docs/Web/API/HTMLElement}

\bibitem{formSubmit} HTMLFormElement.submit() -- Web APIs | MDN. [online] [cit.~13.12.2020]. Dostupné z: \url{https://developer.mozilla.org/en-US/docs/Web/API/HTMLFormElement/submit}

\bibitem{monoProject} Home | Mono. [online] [cit.~18.12.2020]. Dostupné z: \url{https://www.mono-project.com}

\bibitem{yarn} Home | Yarn -- Package Manager. [online] [cit.~14.2.2021]. Dostupné z: \url{https://yarnpkg.com}

\bibitem{nodejsApi} Index | Node.js v15.x Documentation. [online] [cit.~19.12.2020]. Dostupné z: \url{https://nodejs.org/docs/latest-v15.x/api}

\bibitem{winformsObselote4} Is WPF replacement of WinForms? -- Stack Overflow [online] [cit.~18.12.2020]. Dostupné z: \url{https://stackoverflow.com/questions/4852407/is-wpf-replacement-of-winforms/4852581}

\bibitem{katalon} Katalon Recorder (Selenium tests generator) -- Internetový obchod Chrome. [online] [cit.~2.5.2020]. Dostupné z: \url{https://chrome.google.com/webstore/detail/katalon-recorder-selenium/ljdobmomdgdljniojadhoplhkpialdid}

\bibitem{katalonRecorderMainPage} Katalon Recorder IDE. [online] [cit.~16.11.2020]. Dostupné z: \url{https://www.katalon.com/katalon-recorder-ide}

\bibitem{katalonRecorderVsStudio} Katalon Recorder vs Katalon Studio | Katalon Docs. [online] [cit.~17.11.2020]. Dostupné z: \url{https://docs.katalon.com/katalon-recorder/docs/katalon-recorder-vs-katalon-studio.html}

\bibitem{katalonPricing} Katalon Solution -- Pricing. [online] [cit.~16.11.2020]. Dostupné z: \url{https://www.katalon.com/pricing}

\bibitem{katalonRecorderWikipedia} Katalon Studio -- Wikipedia. [online] [cit.~16.11.2020]. Dostupné z: \url{https://en.wikipedia.org/wiki/Katalon_Studio}

\bibitem{interpretingSUS} Measuring and Interpreting System Usability Scale (SUS) -- UIUX Trend. [online] [cit.~17.2.2021]. Dostupné z: \url{https://uiuxtrend.com/measuring-system-usability-scale-sus}

\bibitem{navigator.appName} NavigatorID.appName -- Web APIs | MDN. [online] [cit.~3.11.2020]. Dostupné z: \url{https://developer.mozilla.org/en-US/docs/Web/API/NavigatorID/appName}

\bibitem{npm} npm | build amazing things. [online] [cit.~13.2.2021]. Dostupné z: \url{https://www.npmjs.com}

\bibitem{phantomJsMainPage} PhantomJS -- Scriptable Headless Browser. [online] [cit.~7.11.2020]. Dostupné z: \url{https://phantomjs.org}

\bibitem{playwrightMainPage} Playwright. [online] [cit.~5.11.2020]. Dostupné z: \url{https://playwright.dev}

\bibitem{playwrightApi} playwright/api.md at master · microsoft/playwright · GitHub. [online] [cit.~5.11.2020]. Dostupné z: \url{https://github.com/microsoft/playwright/blob/master/docs/api.md}

\bibitem{playwrightBrowserPatches} playwright/browser\_patches at master · microsoft/playwright · GitHub. [online] [cit.~5.11.2020]. Dostupné z: \url{https://github.com/microsoft/playwright/tree/master/browser_patches}

\bibitem{puppeteerMainPage} Puppeteer. [online] [cit.~2.11.2020]. Dostupné z: \url{https://pptr.dev}

\bibitem{puppeteerApi} puppeteer/api.md at main · puppeteer/puppeteer · GitHub. [online] [cit.~3.11.2020]. Dostupné z: \url{https://github.com/puppeteer/puppeteer/blob/main/docs/api.md}

\bibitem{puppeteerApiPageWaitForNav} puppeteer/api.md\#pagewaitfornavigationoptions v5.5.0 · puppeteer/puppe\-teer · GitHub. [online] [cit.~16.1.2021]. Dostupné z: \url{https://github.com/puppeteer/puppeteer/blob/v5.5.0/docs/api.md#pagewaitfornavigationoptions}

\bibitem{phantomJsFirstRelease} Release 1.0.0 · ariya/phantomjs · GitHub. [online] [cit.~7.11.2020]. Dostupné z: \url{https://github.com/ariya/phantomjs/releases/tag/1.0.0}

\bibitem{seleniumIdeReleses} Releases · SeleniumHQ/selenium-ide · GitHub. [online] [cit.~14.11.2020]. Dostupné z: \url{https://github.com/SeleniumHQ/selenium-ide/releases}

\bibitem{playwrightFirstRelease} Releases · microsoft/playwright · GitHub. [online] [cit.~5.11.2020]. Dostupné z: \url{https://github.com/microsoft/playwright/releases?after=v0.13.0}

\bibitem{puppeteerFirstRelease} Releases · puppeteer/puppeteer · GitHub. [online] [cit.~2.11.2020]. Dostupné z: \url{https://github.com/puppeteer/puppeteer/releases?after=v0.12.0}

\bibitem{firefoxRemoteProtocol} Remote -- MozillaWiki. [online] [cit.~2.11.2020]. Dostupné z: \url{https://wiki.mozilla.org/Remote}

\bibitem{firefoxRemoteProtocol2} Remote Protocol -- Firefox Source Docs documentation. [online] [cit.~2.11.2020]. Dostupné z: \url{https://firefox-source-docs.mozilla.org/remote/index.html}

\bibitem{getActivePagePupppeteer} Request: browser.currentPage() or similar way to access Pages · Issue \#443 · puppeteer/puppeteer · GitHub. [online] [cit.~12.12.2020]. Dostupné z: \url{https://github.com/puppeteer/puppeteer/issues/443}

\bibitem{selectors3W3c} Selectors Level 3. World Wide Web Consortium (W3C). [online] [cit.~9.11.2020]. Dostupné z: \url{https://www.w3.org/TR/selectors-3}

\bibitem{selectors4W3c} Selectors Level 4. World Wide Web Consortium (W3C). [online] [cit.~9.11.2020]. Dostupné z: \url{https://www.w3.org/TR/selectors-4}

\bibitem{seleniumWiki} Selenium (software) -- Wikipedia. [online] [cit.~2.11.2020]. Dostupné z: \url{https://en.wikipedia.org/wiki/Selenium_(software)}

\bibitem{seleniumHistory} Selenium History. SeleniumHQ Browser Automation. [online] [cit.~14.11.2020]. Dostupné z: \url{https://www.selenium.dev/history}

\bibitem{seleniumNodeJsDocs} SeleniumHQ Browser Automation. [online] [cit.~3.11.2020]. Dostupné z: \url{https://www.selenium.dev/selenium/docs/api/javascript}

\bibitem{selenium-ide} Selenium IDE · Open source record and playback test automation for the web. [online] [cit.~30.10.2020]. Dostupné z: \url{https://www.selenium.dev/selenium-ide}

\bibitem{dpiawarenessWinApi} SetProcessDpiAwareness function (shellscalingapi.h) -- Win32 apps | Microsoft Docs. [online] [cit.~13.2.2021]. Dostupné z: \url{https://docs.microsoft.com/en-us/windows/win32/api/shellscalingapi/nf-shellscalingapi-setprocessdpiawareness}

\bibitem{monoSupported} Supported Platforms | Mono. [online] [cit.~21.1.2021]. Dostupné z: \url{https://www.mono-project.com/docs/about-mono/supported-platforms}

\bibitem{sus} System Usability Scale (SUS) | Usability.gov. [online] [cit. 16.2.2021]. Dostupné z: \url{https://www.usability.gov/how-to-and-tools/methods/system-usability-scale.html}

\bibitem{browsingContextW3C} Terminology -- HTML5. W3C on GitHub. [online] [cit.~7.11.2020]. Dostupné z: \url{https://w3c.github.io/html-reference/terminology.html}

\bibitem{seleniumDocs} The Selenium Browser Automation Project -- Documentation for Selenium. [online] [cit.~2.11.2020]. Dostupné z: \url{https://www.selenium.dev/documentation/en}

\bibitem{csharpHistory} The History of C\# | Microsoft Docs. [online] [cit.~18.12.2020]. Dostupné z: \url{https://docs.microsoft.com/en-us/dotnet/csharp/whats-new/csharp-version-history}

\bibitem{typeScript} TypeScript: Typed JavaScript at Any Scale. [online] [cit.~17.12.2020]. Dostupné z: \url{https://www.typescriptlang.org}

\bibitem{headlessFirefox} Using Headless Mode in Firefox -- Mozilla Hacks -- The Web Developer Blog. [online] [cit.~7.11.2020]. Dostupné z: \url{https://hacks.mozilla.org/2017/12/using-headless-mode-in-firefox}

\bibitem{uwpDocs} UWP Documentation -- UWP applications | Microsoft Docs. [online] [cit.~19.12.2020]. Dostupné z: \url{https://docs.microsoft.com/en-us/windows/uwp}

\bibitem{viewport} Viewport Concepts -- CSS | MDN. [online] [cit.~7.5.2020]. Dostupné z: \url{https://developer.mozilla.org/en-US/docs/Web/CSS/Viewport_concepts}

\bibitem{visualStudioMainPage} Visual Studio IDE, Code Editor, Azure DevOps, \& App Center. [online] [cit.~18.12.2020]. Dostupné z: \url{https://visualstudio.microsoft.com}

\bibitem{webstorm} WebStorm: The Smartest JavaScript IDE by JetBrains. [online] [cit.~12.2.2021]. Dostupné z: \url{https://www.jetbrains.com/webstorm}

\bibitem{messageBroker} What are Message Brokers? | IBM. [online] [cit.~28.12.2020]. Dostupné z: \url{https://www.ibm.com/cloud/learn/message-brokers}

\bibitem{extensionAPI1} What are extensions? -- Google Chrome. [online] [cit.~2.5.2020]. Dostupné z: \url{https://developer.chrome.com/extensions}

\bibitem{wpfDocs} What is WPF? -- Visual Studio | Microsoft Docs. [online] [cit.~19.12.2020]. Dostupné z: \url{https://docs.microsoft.com/en-us/visualstudio/designers/getting-started-with-wpf?view=vs-2019}

\bibitem{nodejsCompatibility}
win: block running on EOL Windows versions by joaocgreis · Pull Request \#31954 · nodejs/node · GitHub. [online] [cit.~28.1.2021]. Dostupné z: \url{https://github.com/nodejs/node/pull/31954}

\bibitem{windowObject} Window -- Web APIs | MDN. [online] [cit.~13.12.2020]. Dostupné z: \url{https://developer.mozilla.org/en-US/docs/Web/API/Window}

\bibitem{loadEvent} Window: load event -- Web APIs | MDN. [online] [cit.~5.11.2020]. Dostupné z: \url{https://developer.mozilla.org/en-US/docs/Web/API/Window/load_event}

\bibitem{winformsObselote2} WinForms -- Will Windows Forms be deprecated in favor of WPF? -- Stack Overflow. [online] [cit.~18.12.2020]. Dostupné z: \url{https://stackoverflow.com/questions/913417/will-windows-forms-be-deprecated-in-favor-of-wpf}

\bibitem{winformObselote1} WinForms -- Windows Forms Dead. Long life to WPF -- Stack Overflow. [online] [cit.~18.12.2020]. Dostupné z: \url{https://stackoverflow.com/questions/2632118/windows-forms-dead-long-life-to-wpf}

\bibitem{winformsObselote3} WPF -- Are Windows Forms old tech? -- Stack Overflow. [online] [cit.~18.12.2020]. Dostupné z: \url{https://stackoverflow.com/questions/1916510/are-windows-forms-old-tech}

\bibitem{zeromq} ZeroMQ. [online] [cit.~19.12.2020]. Dostupné z: \url{https://zeromq.org}

\bibitem{zeromqCSharp} ZeroMQ | C\#. [online] [cit.~19.12.2020]. Dostupné z: \url{https://zeromq.org/languages/csharp}

\bibitem{zeromqDocs} ZeroMQ | Get started. [online] [cit.~19.12.2020]. Dostupné z: \url{https://zeromq.org/get-started}


\end{thebibliography}
\end{flushleft}
\setstretch{1.2}
\newpage