\newpage
\setstretch{1.0}
\begin{thebibliography}{99}
\addcontentsline{toc}{section}{Reference}

\bibitem{dotnetApi} .NET API browser | Microsoft Docs. [online]. Copyright~©~Microsoft 2020 [cit.~19.12.2020]. Dostupné z: \url{https://docs.microsoft.com/en-us/dotnet/api/?view=netframework-4.8}

\bibitem{winformsObselote5} .net - When creating a new GUI, is WPF the preferred choice over Windows Forms? - Stack Overflow. Stack Overflow - Where Developers Learn, Share, \& Build Careers [online] [cit.~18.12.2020]. Dostupné z: \url{https://stackoverflow.com/questions/57909/when-creating-a-new-gui-is-wpf-the-preferred-choice-over-windows-forms}

\bibitem{seleniumWhyUse} 16 reasons why to use Selenium IDE in 2019 (and 2 why not) - Automated Visual Testing | Applitools. Automated Visual Testing with Visual AI [online]. Copyright~©~2020 Applitools. All Rights Reserved. [cit.~14.11.2020]. Dostupné z: \url{https://applitools.com/blog/why-selenium-ide-2019}

\bibitem{seleniumAbout} About Selenium. SeleniumHQ Browser Automation [online] [cit.~2.5.2020]. Dostupné z: \url{https://www.selenium.dev/about}

\bibitem{nodejs} About | Node.js. [online]. Copyright~©~OpenJS Foundation. All Rights Reserved. Portions of this site originally [cit.~30.10.2020]. Dostupné z: \url{https://nodejs.org/en/about}

\bibitem{phantomJsArchiving} Archiving the project: suspending the development · Issue \#15344 · ariya/phantomjs · GitHub. GitHub: Where the world builds software · GitHub [online]. Copyright~©~2020 GitHub, Inc. [cit.~7.11.2020]. Dostupné z: \url{https://github.com/ariya/phantomjs/issues/15344}

\bibitem{headless} Automated testing with Headless Chrome  |  Web  |  Google Developers. Google Developers [online] [cit.~2.5.2020]. Dostupné z: \url{https://developers.google.com/web/updates/2017/06/headless-karma-mocha-chai}

\bibitem{browsingContextMozillaDevs} Browsing context - MDN Web Docs Glossary: Definitions of Web-related terms | MDN. [online]. Copyright~©~2005 [cit.~7.11.2020]. Dostupné z: \url{https://developer.mozilla.org/en-US/docs/Glossary/Browsing_context}

\bibitem{uwpSupportedPlatforms} Choose your Windows app platform - Windows applications | Microsoft Docs. [online]. Copyright~©~Microsoft 2020 [cit.~19.12.2020]. Dostupné z: \url{https://docs.microsoft.com/en-us/windows/apps/desktop/choose-your-platform}

\bibitem{extensionAPI2} Chrome APIs - Google Chrome. [online] [cit.~2.5.2020]. Dostupné z: \url{https://developer.chrome.com/extensions/api_index}

\bibitem{devtools} Chrome DevTools  |  Google Developers. Google Developers [online] [cit.~	2.5.2020]. Dostupné z: 	\url{https://developers.google.com/web/tools/chrome-devtools}

\bibitem{devtoolsProtocol} Chrome DevTools Protocol [online] [cit.~2.11.2020]. Dostupné z: \url{https://chromedevtools.github.io/devtools-protocol}

\bibitem{ranorexAbout} Company Profile | About Ranorex. Test Automation for GUI Testing | Ranorex [online]. Copyright~©~2020 Ranorex GmbH. All Rights Reserved [cit.~9.12.2020]. Dostupné z: \url{https://www.ranorex.com/company}

\bibitem{monoCompatibility} Compatibility | Mono. Home | Mono [online]. Copyright~©~2020 Mono Project [cit.~19.12.2020]. Dostupné z: \url{https://www.mono-project.com/docs/about-mono/compatibility}

\bibitem{seleniumEcosystem} Ecosystem. SeleniumHQ Browser Automation [online] [cit.~31.10.2020]. Dostupné z: \url{https://www.selenium.dev/ecosystem}

\bibitem{electron} Electron | Build cross-platform desktop apps with JavaScript, HTML, and CSS. [online] [cit.~14.11.2020]. Dostupné z: \url{https://www.electronjs.org}

\bibitem{elementObject} Element - Web APIs | MDN. [online]. Copyright~©~2005 [cit.~13.12.2020]. Dostupné z: \url{https://developer.mozilla.org/en-US/docs/Web/API/Element}

\bibitem{firefoxReleaseCalendar} Firefox Release Calendar - MozillaWiki. [online] [cit.~8.11.2020]. Dostupné z: \url{https://wiki.mozilla.org/Release_Management/Calendar}

\bibitem{firefoxLegacyExtensions} Frequently asked questions - Firefox add-on technology is modernizing | Firefox Help [online]. Copyright ©1998 [cit.~14.11.2020]. Dostupné z: \url{https://support.mozilla.org/en-US/kb/frequently-asked-questions-firefox-addon}

\bibitem{headlessChromeGettingStarted} Getting Started with Headless Chrome  |  Web  |  Google Developers. Google Developers [online] [cit.~7.11.2020]. Dostupné z: \url{https://developers.google.com/web/updates/2017/04/headless-chrome}

\bibitem{seleniumIdeGithub} GitHub - SeleniumHQ/selenium-ide at v3. GitHub: Where the world builds software · GitHub [online]. Copyright~©~2020 GitHub, Inc. [cit.~14.11.2020]. Dostupné z: \url{https://github.com/SeleniumHQ/selenium-ide/tree/v3}

\bibitem{checkly} GitHub - checkly/headless-recorder: Headless recorder is a~Chrome extension that records your browser interactions and generates a~Puppeteer or Playwright script.. GitHub: Where the world builds software · GitHub [online]. Copyright~©~2020 GitHub, Inc. [cit.~30.10.2020]. Dostupné z: \url{https://github.com/checkly/headless-recorder}

\bibitem{scintillaGithub} GitHub - jacobslusser/ScintillaNET: A Windows Forms control, wrapper, and bindings for the Scintilla text editor.. GitHub: Where the world builds software · GitHub [online]. Copyright~©~2021 GitHub, Inc. [cit.~14.1.2021]. Dostupné z: \url{https://github.com/jacobslusser/ScintillaNET}

\bibitem{playwrightGithub} GitHub - microsoft/playwright: Node.js library to automate Chromium, Firefox and WebKit with a~single API. GitHub: Where the world builds software · GitHub [online]. Copyright~©~2020 GitHub, Inc. [cit.~5.11.2020]. Dostupné z: \url{https://github.com/microsoft/playwright}

\bibitem{crlzmq4} GitHub - zeromq/clrzmq4: ZeroMQ C\# namespace (.NET and mono, Windows, Linux and MacOSX, x86 and amd64). GitHub: Where the world builds software · GitHub [online]. Copyright~©~2020 GitHub, Inc. [cit.~19.12.2020]. Dostupné z: \url{https://github.com/zeromq/clrzmq4}

\bibitem{netmqGithub} GitHub - zeromq/netmq: A 100\% native C\# implementation of ZeroMQ for .NET. GitHub: Where the world builds software · GitHub [online]. Copyright~©~2020 GitHub, Inc. [cit.~19.12.2020]. Dostupné z: \url{https://github.com/zeromq/netmq}

\bibitem{zeromqJs} GitHub - zeromq/zeromq.js: Node.js bindings to the ØMQ library. GitHub: Where the world builds software · GitHub [online]. Copyright~©~2020 GitHub, Inc. [cit.~19.12.2020]. Dostupné z: \url{https://github.com/zeromq/zeromq.js}

\bibitem{googleChromeReleases} Google Chrome version history - Wikipedia. [online] [cit.~8.11.2020]. Dostupné z: \url{https://en.wikipedia.org/wiki/Google_Chrome_version_history}

\bibitem{htmlElementObject} HTMLElement - Web APIs | MDN. [online]. Copyright~©~2005 [cit.~13.12.2020]. Dostupné z: \url{https://developer.mozilla.org/en-US/docs/Web/API/HTMLElement}

\bibitem{formSubmit} HTMLFormElement.submit() - Web APIs | MDN. [online]. Copyright~©~2005 [cit.~13.12.2020]. Dostupné z: \url{https://developer.mozilla.org/en-US/docs/Web/API/HTMLFormElement/submit}

\bibitem{monoProject} Home | Mono. Home | Mono [online]. Copyright~©~2020 Mono Project [cit.~18.12.2020]. Dostupné z: \url{https://www.mono-project.com}

\bibitem{nodejsApi} Index | Node.js v15.4.0 Documentation. [online] [cit.~19.12.2020]. Dostupné z: \url{https://nodejs.org/api}

\bibitem{seleniumNodeJsDocs} Index. SeleniumHQ Browser Automation [online] [cit.~3.11.2020]. Dostupné z: \url{https://www.selenium.dev/selenium/docs/api/javascript}

\bibitem{winformsObselote4} Is WPF replacement of WinForms? - Stack Overflow. Stack Overflow - Where Developers Learn, Share, \& Build Careers [online] [cit.~18.12.2020]. Dostupné z: \url{https://stackoverflow.com/questions/4852407/is-wpf-replacement-of-winforms/4852581}

\bibitem{katalon} Katalon Recorder (Selenium tests generator) - Internetový obchod Chrome. [online] [cit.~2.5.2020]. Dostupné z: \url{https://chrome.google.com/webstore/detail/katalon-recorder-selenium/ljdobmomdgdljniojadhoplhkpialdid}

\bibitem{katalonRecorderVsStudio} Katalon Recorder vs Katalon Studio | Katalon Docs. Redirecting… [online]. Copyright~©~2020 Katalon LLC. All rights reserved. [cit.~17.11.2020]. Dostupné z: \url{https://docs.katalon.com/katalon-recorder/docs/katalon-recorder-vs-katalon-studio.html}

\bibitem{katalonRecorderMainPage} Katalon Solution. Katalon Solution [online]. Copyright~©~2020 Katalon LLC. All rights reserved. [cit.~16.11.2020]. Dostupné z: \url{https://www.katalon.com/katalon-recorder-ide}

\bibitem{katalonPricing} Katalon Solution. Katalon Solution [online]. Copyright~©~2020 Katalon LLC. All rights reserved. [cit.~16.11.2020]. Dostupné z: \url{https://www.katalon.com/pricing}

\bibitem{katalonRecorderWikipedia} Katalon Studio - Wikipedia. [online] [cit.~16.11.2020]. Dostupné z: \url{https://en.wikipedia.org/wiki/Katalon_Studio}

\bibitem{navigator.appName} NavigatorID.appName - Web APIs | MDN. [online]. Copyright~©~2005 [cit.~3.11.2020]. Dostupné z: \url{https://developer.mozilla.org/en-US/docs/Web/API/NavigatorID/appName}

\bibitem{phantomJsMainPage} PhantomJS - Scriptable Headless Browser. PhantomJS - Scriptable Headless Browser [online]. Copyright~©~2010 [cit.~7.11.2020]. Dostupné z: \url{https://phantomjs.org}

\bibitem{playwrightMainPage} Playwright. Playwright [online] [cit.~5.11.2020]. Dostupné z: \url{https://playwright.dev}

\bibitem{puppeteerMainPage} Puppeteer [online] [cit.~2.11.2020]. Dostupné z: \url{https://pptr.dev}

\bibitem{phantomJsFirstRelease} Release 1.0.0 · ariya/phantomjs · GitHub. GitHub: Where the world builds software · GitHub [online]. Copyright~©~2020 GitHub, Inc. [cit.~7.11.2020]. Dostupné z: \url{https://github.com/ariya/phantomjs/releases/tag/1.0.0}

\bibitem{seleniumIdeReleses} Releases · SeleniumHQ/selenium-ide · GitHub. GitHub: Where the world builds software · GitHub [online]. Copyright~©~2020 GitHub, Inc. [cit.~14.11.2020]. Dostupné z: \url{https://github.com/SeleniumHQ/selenium-ide/releases}

\bibitem{playwrightFirstRelease} Releases · microsoft/playwright · GitHub. GitHub: Where the world builds software · GitHub [online]. Copyright~©~2020 GitHub, Inc. [cit.~5.11.2020]. Dostupné z: \url{https://github.com/microsoft/playwright/releases?after=v0.13.0}

\bibitem{puppeteerFirstRelease} Releases · puppeteer/puppeteer · GitHub. GitHub: Where the world builds software · GitHub [online]. Copyright~©~2020 GitHub, Inc. [cit.~2.11.2020]. Dostupné z: \url{https://github.com/puppeteer/puppeteer/releases?after=v0.12.0}

\bibitem{firefoxRemoteProtocol} Remote - MozillaWiki. [online] [cit.~2.11.2020]. Dostupné z: \url{https://wiki.mozilla.org/Remote}

\bibitem{firefoxRemoteProtocol2} Remote Protocol — Firefox Source Docs documentation. Firefox Source Tree Documentation — Firefox Source Docs documentation [online] [cit.~2.11.2020]. Dostupné z: \url{https://firefox-source-docs.mozilla.org/remote/index.html}

\bibitem{getActivePagePupppeteer} Request: browser.currentPage() or similar way to access Pages · Issue \#443 · puppeteer/puppeteer · GitHub. GitHub: Where the world builds software · GitHub [online]. Copyright~©~2020 GitHub, Inc. [cit.~12.12.2020]. Dostupné z: \url{https://github.com/puppeteer/puppeteer/issues/443}

\bibitem{selectors3W3c} Selectors Level 3. World Wide Web Consortium (W3C) [online]. Copyright~©~2018 [cit.~9.11.2020]. Dostupné z: \url{https://www.w3.org/TR/selectors-3}

\bibitem{selectors4W3c} Selectors Level 4. World Wide Web Consortium (W3C) [online]. Copyright~©~2018 [cit.~9.11.2020]. Dostupné z: \url{https://www.w3.org/TR/selectors-4}

\bibitem{seleniumWiki} Selenium (software) - Wikipedia. [online] [cit.~2.11.2020]. Dostupné z: \url{https://en.wikipedia.org/wiki/Selenium_(software)}

\bibitem{seleniumHistory} Selenium History. SeleniumHQ Browser Automation [online] [cit.~14.11.2020]. Dostupné z: \url{https://www.selenium.dev/history}

\bibitem{selenium-ide} Selenium IDE · Open source record and playback test automation for the web. SeleniumHQ Browser Automation [online]. Copyright~©~2019 Software Freedom Conservancy [cit.~30.10.2020]. Dostupné z: \url{https://www.selenium.dev/selenium-ide}

\bibitem{browsingContextW3C} Terminology - HTML5. W3C on GitHub [online] [cit.~7.11.2020]. Dostupné z: \url{https://w3c.github.io/html-reference/terminology.html}

\bibitem{seleniumDocs} The Selenium Browser Automation Project :: Documentation for Selenium [online] [cit.~2.11.2020]. Dostupné z: \url{https://www.selenium.dev/documentation/en}

\bibitem{csharpHistory} The history of C\# - C\# Guide | Microsoft Docs. [online]. Copyright~©~Microsoft 2020 [cit.~18.12.2020]. Dostupné z: \url{https://docs.microsoft.com/en-us/dotnet/csharp/whats-new/csharp-version-history}

\bibitem{typeScript} TypeScript: Typed JavaScript at Any Scale.. TypeScript: Typed JavaScript at Any Scale. [online]. Copyright~©~2012 [cit.~17.12.2020]. Dostupné z: \url{https://www.typescriptlang.org}

\bibitem{uwpDocs} UWP Documentation - UWP app developer - UWP applications | Microsoft Docs. [online]. Copyright~©~Microsoft 2020 [cit.~19.12.2020]. Dostupné z: \url{https://docs.microsoft.com/en-us/windows/uwp}

\bibitem{headlessFirefox} Using Headless Mode in Firefox - Mozilla Hacks - the Web developer blog. Home - Mozilla Hacks - the Web developer blog [online] [cit.~7.11.2020]. Dostupné z: \url{https://hacks.mozilla.org/2017/12/using-headless-mode-in-firefox}

\bibitem{viewport} Viewport concepts - CSS: Cascading Style Sheets | MDN. [online]. Copyright~©~2005 [cit.~7.5.2020]. Dostupné z: \url{https://developer.mozilla.org/en-US/docs/Web/CSS/Viewport_concepts}

\bibitem{visualStudioMainPage} Visual Studio IDE, Code Editor, Azure DevOps, \& App Center - Visual Studio. [online] [cit.~18.12.2020]. Dostupné z: \url{https://visualstudio.microsoft.com}

\bibitem{messageBroker} What are Message Brokers? | IBM. [online]. Copyright~©~Copyright IBM Corporation 2020 [cit.~28.12.2020]. Dostupné z: \url{https://www.ibm.com/cloud/learn/message-brokers}

\bibitem{extensionAPI1} What are extensions? - Google Chrome. [online] [cit.~2.5.2020]. Dostupné z: \url{https://developer.chrome.com/extensions}

\bibitem{wpfDocs} What is WPF? - Visual Studio | Microsoft Docs. [online]. Copyright~©~Microsoft 2020 [cit.~19.12.2020]. Dostupné z: \url{https://docs.microsoft.com/en-us/visualstudio/designers/getting-started-with-wpf?view=vs-2019}

\bibitem{windowObject} Window - Web APIs | MDN. [online]. Copyright~©~2005 [cit.~13.12.2020]. Dostupné z: \url{https://developer.mozilla.org/en-US/docs/Web/API/Window}

\bibitem{loadEvent} Window: load event - Web APIs | MDN. [online]. Copyright~©~2005 [cit.~5.11.2020]. Dostupné z: \url{https://developer.mozilla.org/en-US/docs/Web/API/Window/load_event}

\bibitem{zeromq} ZeroMQ [online]. Copyright~©~2020 The ZeroMQ authors [cit.~19.12.2020]. Dostupné z: \url{https://zeromq.org}

\bibitem{zeromqCSharp} ZeroMQ | C\# [online]. Copyright~©~2020 The ZeroMQ authors [cit.~19.12.2020]. Dostupné z: \url{https://zeromq.org/languages/csharp}

\bibitem{zeromqDocs} ZeroMQ | Get started [online]. Copyright~©~2020 The ZeroMQ authors [cit.~19.12.2020]. Dostupné z: \url{https://zeromq.org/get-started}

\bibitem{enableTrueRemoteDebuggingChrome} google chrome - Using Chromium Remote Debugging from External Device - Stack Overflow. Stack Overflow - Where Developers Learn, Share, \& Build Careers [online] [cit.~4.1.2021]. Dostupné z: \url{https://stackoverflow.com/questions/18506233/using-chromium-remote-debugging-from-external-device}

\bibitem{playwrightApi} playwright/api.md at master · microsoft/playwright · GitHub. GitHub: Where the world builds software · GitHub [online]. Copyright~©~2020 GitHub, Inc. [cit.~5.11.2020]. Dostupné z: \url{https://github.com/microsoft/playwright/blob/master/docs/api.md}

\bibitem{playwrightBrowserPatches} playwright/browser\_patches at master · microsoft/playwright · GitHub. GitHub: Where the world builds software · GitHub [online]. Copyright~©~2020 GitHub, Inc. [cit.~5.11.2020]. Dostupné z: \url{https://github.com/microsoft/playwright/tree/master/browser_patches}

\bibitem{puppeteerApi} puppeteer/api.md at main · puppeteer/puppeteer · GitHub. GitHub: Where the world builds software · GitHub [online]. Copyright~©~2020 GitHub, Inc. [cit.~3.11.2020]. Dostupné z: \url{https://github.com/puppeteer/puppeteer/blob/main/docs/api.md}

\bibitem{puppeteerApiPageWaitForNav} puppeteer/api.md at v5.5.0 · puppeteer/puppeteer · GitHub. GitHub: Where the world builds software · GitHub [online]. Copyright~©~2021 GitHub, Inc. [cit.~16.1.2021]. Dostupné z: \url{https://github.com/puppeteer/puppeteer/blob/v5.5.0/docs/api.md#pagewaitfornavigationoptions}

\bibitem{winformsObselote2} winforms - Will Windows Forms be deprecated in favor of WPF? - Stack Overflow. Stack Overflow - Where Developers Learn, Share, \& Build Careers [online] [cit.~18.12.2020]. Dostupné z: \url{https://stackoverflow.com/questions/913417/will-windows-forms-be-deprecated-in-favor-of-wpf}

\bibitem{winformObselote1} winforms - Windows Forms Dead. Long life to WPF - Stack Overflow. Stack Overflow - Where Developers Learn, Share, \& Build Careers [online] [cit.~18.12.2020]. Dostupné z: \url{https://stackoverflow.com/questions/2632118/windows-forms-dead-long-life-to-wpf}

\bibitem{winformsObselote3} wpf - Are Windows Forms old tech? - Stack Overflow. Stack Overflow - Where Developers Learn, Share, \& Build Careers [online] [cit.~18.12.2020]. Dostupné z: \url{https://stackoverflow.com/questions/1916510/are-windows-forms-old-tech}


\end{thebibliography}
\setstretch{1.2}
\newpage